---
title: "Online appendix"
author: "Martin G. Søyland"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: pdf_document

---
\fontsize{8}{22}
\renewcommand{\baselinestretch}{.5}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
theme_set(theme_bw())
```
## How to get data
The data is located in the github repository "https://github.com/martigso/ministersNor/". For those familiar with github, cloning the the repository and running "online_appendix.Rmd" should produce this document (here done through R):

```{r getData, eval=FALSE}
system("cd <where/to/put/the/repository>")

system("git clone git@github.com:martigso/ministersNor.git")
```

## Prepping data
In order to load the data, the preferred way for for R-users is to use the .rda-file. There is, however, also a .csv-file available in the repository for those that do not use R. Further, a the parliamentary experience and youth party experience variable needs to be recoded in order to reproduce the results:
```{r prep, eval=TRUE, warning=FALSE,error=FALSE}
load("./data/ministers.rda")
ministers$youthAny <- ifelse(ministers$youthCen==1 | ministers$youthLoc==1, 1, 0)
ministers$parlTen_cum2 <- ifelse(ministers$parlTen_cum > 31, 1, 0)
source("./thesis/R/getmode.R")
```


## The paper models
All models from the paper is replicated below. These models require the _survival_-package to run:
```{r prim_mods}
library(survival)
```

### Base model

```{r base}
base <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls + age_cen +
                factor(gender) + factor(education_dum) +
                frailty(jurisdiction),
              data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(base)[["coefficients"]], digits = 3)
```

### Including experience
```{r experience}
experience <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls +
                      age_cen + factor(gender) + factor(education_dum) +
                      factor(youthAny) + minister_exp_cum_y_lag + factor(parlTen_cum2) +
                      frailty(jurisdiction),
                    data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(experience)[["coefficients"]], digits = 3)
```

### Cabinet attributes

```{r cabinet}
cab <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls +
               age_cen + factor(gender) + factor(education_dum) +
               factor(CabinetType) + factor(structure)+
               frailty(jurisdiction),
             data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(cab)[["coefficients"]], digits = 3)
```


### Full model
```{r all}
all <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls + age_cen + factor(gender) +
               factor(youthAny) + minister_exp_cum_y_lag + factor(parlTen_cum2) +
               factor(education_dum) +  factor(CabinetType) + factor(structure) +
               frailty(jurisdiction),
             data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(all)[["coefficients"]], digits = 3)
```


## Robustness models

### Age squared
```{r agesq}
agesq <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls +
                 poly(age_cen, 2, raw = FALSE) + factor(gender) +
                 factor(youthAny) + minister_exp_cum_y_lag + factor(parlTen_cum2) +
                 factor(education_dum) +  factor(CabinetType) + factor(structure) +
                 frailty(jurisdiction),
               data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(agesq)[["coefficients"]], digits = 3)

```

The close to linear relationship between durability and age squared can easily be shown by ploting the regression line for each value on age:
```{r agesqplot}
pred1 <- with(ministers, data.frame(resigcalls=min(resigcalls),
                                age_cen=round(min(age_cen),
                                              digits = 0):round(max(age_cen),
                                                                digits = 0),
                                gender=getmode(gender),
                                minister_exp_cum_y_lag=median(minister_exp_cum_y_lag),
                                parlTen_cum2=getmode(parlTen_cum2),
                                youthAny=getmode(youthAny),
                                education_dum=getmode(education_dum),
                                CabinetType=getmode(CabinetType),
                                structure=getmode(structure)))

pred_plot <- data.frame(predict(agesq, newdata=pred1,
                                type="risk", se=TRUE, reference="sample"), pred1)

pred_plot$upper <- pred_plot$fit+1.96*pred_plot$se.fit
pred_plot$lower <- pred_plot$fit-1.96*pred_plot$se.fit
pred_plot$age_cen <- pred_plot$age_cen + median(ministers$age)

library(ggplot2)

ggplot(pred_plot, aes(x=age_cen, y=fit))+
  geom_line(stat="identity", color="black")+
  geom_ribbon(aes(ymax=upper, ymin=lower, color=NULL), alpha=.2, fill="black") +
  geom_hline(aes(yintercept=1), linetype="dashed")+
  labs(y="Hazard Ratios", x="Age")+
  scale_x_continuous(breaks=seq(0,100,5), expand=c(0,0))+
  scale_y_continuous(breaks=seq(0,10,.5), expand=c(0,.21))+
  theme(legend.position=c(.15,.9),
        panel.grid.major.x=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        strip.background=element_blank(),
        panel.margin=unit(1, "cm"),
        axis.line.x=element_line(),
        axis.line.y=element_line(),
        axis.title.y=element_text(vjust=1.5, siz=12),
        axis.title.x=element_text(vjust=0, size=12))
```

### Parliamentary experience == in parliament > 0 days
The following example shows how parliamentary experience does matter when it is coded as 1 when a minister has been in parliament more than 0 days:
```{r parl_onday}
ministers$parlTen_cum3 <- ifelse(ministers$parlTen_cum > 0, 1, 0)
parl_onday <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls + age_cen +
                      factor(gender) + factor(youthAny) + minister_exp_cum_y_lag +
                      factor(parlTen_cum3) + factor(education_dum) +  
                      factor(CabinetType) + factor(structure) + frailty(jurisdiction),
                    data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(parl_onday)[["coefficients"]], digits = 3)
```

### Seats and reshuffles
Following Huber and Martinez-Gallardo (2008), I test the whether adverse selection could have a limiting effect on resignation calls by including party size of the minister and reshuffles (Kam and Indridason 2005). 1 indicates that the minister has been reshuffled in this cabinet, and 0 that he has not:
```{r reshuffles}
reshuffles <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls + age_cen +
                      factor(gender) + factor(youthAny) + minister_exp_cum_y_lag +
                      factor(parlTen_cum2) + factor(education_dum) +  
                      factor(CabinetType) + factor(structure) + factor(reshuffle)+
                      frailty(jurisdiction),
                    data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(reshuffles)[["coefficients"]], digits = 3)
```


```{r getSeats}
# This will download some data on first run
if(any(grepl(".html", list.files("./data/seats/")))==FALSE){
  source("./data/seats/getseats.R")
}
load("./data/seats/seats.rda")

ministers <- merge(x = ministers, y = seats, by.x = c("party", "election_year"),
                   by.y = c("party_name", "election_year"), all.x = TRUE)

seats <- coxph(Surv(dur_start, dur_end, event2) ~ resigcalls + age_cen +
                      factor(gender) + factor(youthAny) + minister_exp_cum_y_lag +
                      factor(parlTen_cum2) + factor(education_dum) +  
                      factor(CabinetType) + factor(structure) + seats +
                      frailty(jurisdiction),
                    data=ministers, subset=prime_minister==0 & nsd_id!=299)
round(summary(seats)[["coefficients"]], digits = 3)
```





## Resiganation call coding scheme
The table below shows the search strings for aquiring the resignation calls. Importantly, the matched articles were read and subjectively evaluated to be a resignation call or not -- not all matched articles were counted as resignation calls.

| Fixed string          | Varying string        |
|:----------------------|:----------------------|
| "[Minister name]" AND | "gå\* av\*"           |
|                       | "må\* gå\*"           |
|                       | "bør\* gå \*"         |
|                       | "burde\* gå \*"       |
|                       | "skulle\* gå \*"      |
|                       | "trekke\* seg"        |
|                       | "avgang\*"            |
|                       | "avskjed\*"           |
|                       | "vurder\* sin"        |
|                       | "vurder\* stilling\*" |
|                       | "vurder\* posisjon\*" |
|                       | "fratre\*"            |
|                       | "takk\* av"           |
|                       | "tre\* tilb\*"        |
|                       | "avsett\*"            |
|                       | "avsatt"              |
|                       | "skift\* ut"          |
|                       | "mistill\*"           |

## Ministerial jurisdiction categorization
| __Jurisdiction__     | __Title (ENG) – Minister of...__          | __Title (NOR)__                          |
|:---------------------|:------------------------------------------|:-----------------------------------------|
|__Administration__    | Government Administration                 | Administrasjonsminister                  |
|                      | Labour and Government Administration      | Arbeids- og administrasjonsminister      |
|                      | Labour and Social Inclusion               | Arbeids- og inkluderingsminister         |
|                      | Consumption and Government Administration | Forbruker- og administrasjonsminister    |
|                      | Supply and Reconstruction                 | Forsyning- og gjenreisningsminister      |
|                      | Reform                                    | Fornyingsminister                        |
|                      | Planning                                  | Planleggingsminister                     |
|                      | Labour                                    | Arbeidsminister                          |
|                      | Ministers without portfolio               | Minister uten portefølje                 |
| __Agriculture__      | Agriculture                               | Landbruksminister                        |
| __Culture__          | Culture                                   | Kulturminister                           |
| __Defense__          | Defense                                   | Forsvarsminister                         |
| __Education__        | Research and Higher Education             | Forsknings- og høyere utd.sminister      |
|                      | Education and Church Affairs              | Kirke- og undervisningsminister          |
|                      | Education and Research                    | Kunnskapsminister                        |
| __Environment__      | the Environment                           | Miljøvernminister                        |
| __Finance__          | Finance                                   | Finansminister                           |
|                      | Prices                                    | Prisminister                             |
| __Foreign affairs__  | International Development                 | Bistandsminister                         |
|                      | Human Rights                              | Menneskerettighetsminister               |
|                      | Foreign Affairs                           | Utenriksminister                         |
|                      | International Development                 | Utviklingsminister                       |
| __Health__           | Health                                    | Helseminister                            |
| __Industry__         | Industry                                  | Industriminister                         |
|                      | Trade and Industry                        | Næringsminister                          |
|                      | Petroleum and Energy                      | Olje- og energiminister                  |
| __Justice__          | Justice                                   | Justisminister                           |
| __Regional__         | Local Government                          | Kommunalminister                         |
|                      | Rebuilding Finnmark                       | Minister for gjenoppb. av Finnmark       |
| __Sea and fish__     | Fisheries                                 | Fiskeriminister                          |
|                      | Maritime Law                              | Havrettsminister                         |
|                      | Shipping                                  | Skipsfartsminister                       |
| __Social__           | Children and Family Affairs               | Barne- og familieminister                |
|                      | Family Affairs and Consumption            | Familie- og forbruksminister             |
|                      | Social Affairs                            | Sosialminister                           |
| __Trade__            | Trade                                     | Handelsminister                          |
| __Transport__        | Transport and Communications              | Samferdselsminister                      |

